---
title: "SDL_Harmonization"
author: "Delin Sun"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up Packages
```{r, include=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse) # for data manipulation
library(lme4) # for linear mixed regression models
library(lmerTest)# for p-value of lme4's models
library(afex) # for repeated-measures ANOVA
library(rstatix) # for repeated-measures ANOVA
library(multcomp) # multiple comparisons
library(emmeans) # pairwise-comparisons
library(ggsci)
library(RColorBrewer) # for some extra colours in one of the graphs
library(table1) # make Table 1, mainly demographic & clinical info
library(sjPlot) # plot interactions of lm/lmer outputs
library(ggpubr) # plot multiple panels
library(reshape2) # including melt function to plot heatmaps
#library(brainGraph) # brain atlases & brain graph analyses
```

### (0) functions for analyses
```{r,echo=FALSE}
#######################################################################
# a funciton to change outliers to NA, and NA to group mean in a column
SDL_RmOut <- function(col){
  Q <- quantile(col,na.rm=TRUE) # quantile, IQR = 75% - 25%
  low <- Q[2]-1.5*(Q[4]-Q[2]) # lower limit = 25% - 1.5*IQR
  up  <- Q[4]+1.5*(Q[4]-Q[2]) # upper limit = 75% + 1.5*IQR
  col[col<low | col>up] <- NA # outlier are changed to NA
  col[is.na(col)] <- mean(col,na.rm=T) # impute with group mean
  col
}
#######################################################################


#######################################################################
# a function to model (lm or lmer) data for each ROI, and extract models/coefficients/p-values of models
# Input
# --- y, dataframe column, e.g. df$col01, or select(col1:col10)
# --- df, dataframe
# --- Otype, the type of outputs, e.g. "model", "coef", and "p"
# --- ftxt, text for the formula, e.g. "lmer(formula = y ~ age_d + age_m + drinking_class + sex + race + ses + fh_alc_density + life_trauma_RP + (1|participant_id)"
# --- fterms, which factor to be plotted
# --- fxy, x and y labels
# Output
# --- model, list of models
# --- coef,  matrix of coefficients
# --- pval,  matrix of coefficients
# --- plt,   list of plotting objects
SDL_lm <- function(y,df,Otype,ftxt,fterms=NULL,fxy=NULL){
  model <- eval(parse(text=paste(substr(ftxt,1,nchar(ftxt)-1),", data = df)")))
  coef  <- model %>% summary() %>% coefficients()
  pval  <- coef  %>% .[,"Pr(>|t|)"]
  plt   <- model %>% plot_model(type = "pred", terms = fterms, title = "", axis.title = fxy)
  switch(Otype,"model"=return(list(model)),"coef"=return(list(coef)),"pval"=return(pval),"plt"=return(list(plt)))
}
##############################################################################


##############################################################################
# A function to extract the values of designated parameter from the models worked out by the SDL_lm function
# Input
# --- model, model per ROI worked out by SDL_lm function
# --- para, parameters to be extracted, including
#          "Estimate", "Std. Error", "df", "t value", and "Pr(>|t|)", or
#           1,2,3,4,5,6, in fatc, 3&4 are df1&df2
# Output
# --- mat, a matrix of extracted values, row=factor name, col=ROI name
SDL_cp <- function(model,para="Pr(>|t|)"){
  coef  <- model %>% summary() %>% coefficients()
  mat  <- coef  %>% .[,para]
  return(mat)
}
##############################################################################


#######################################################################
# a function to plot heatmap for matrix of coefficients or p-values
# Input
# --- x, a vector, e.g. Pval0['Group',]
# --- title, title of the coclor bar, e.g. 'P-val (FDR corr.)'
# --- fmidpoint, mid point of the color bar, e.g. 0.05
# --- flimit, min and max of the color bar, e.g. c(0,1)
# --- roi, rois (part or all of the 90 regions) to show
# Output
# --- a heatmap representing the input matrix
SDL_mheat <- function(x,title='Pearson Correlation',fmidpoint=0,flimit=c(-1,1),roi=NULL){
    # corr. coef. matrix
  n <- 4 # 4 harmonization approaches
  m <- matrix(data=0, nrow=n, ncol=n)
  m[lower.tri(m, diag=FALSE)] <- x
  m <- t(m)
  m[lower.tri(m, diag=FALSE)] <- x
  
  roinames <- c('LME(int)', 'LME(int+slp)', 'ComBat', 'ComBat-GAM')
  rownames(m) <- roinames
  colnames(m) <- roinames

  if (!is.null(roi)){m <- m[roi, roi]} # plot selected rois

  # ggplot2 shows heatmap
  mm <- melt(m)
  
  # head(mm)
  mm %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = fmidpoint, limit = flimit, space = "Lab", name=title) +theme_minimal()+ theme(axis.text.x =element_text(angle = 90, vjust = 1, size = 12, hjust = 1))+coord_fixed()
}
#######################################################################

##############################################################################
# Load coordinates of Destrieux atlas (74 L + 74 R)
atlas <- read.csv("..\\Original\\atlas-label.csv",header=T,sep=",")
##############################################################################


##############################################################################
# a function to show heatmap of differences in coef.
### for Fig. 4D,5D,6D,7D,8D
# Input
# --- coef_df, df of regression coefficients
# Output
# --- plot a heatmap of pairwise comparisons of coefficients
SDL_heatmap_coef <- function(coef_df){
  # show the ANOVA results
  a <- coef_df %>% rename('LME(int)'='LME', 'LME(int+slp)'='LME+Slope') %>% mutate(ROI=rownames(.)) %>% pivot_longer(!ROI, names_to = "Method", values_to = "coef") %>% aov_ez("ROI", "coef", ., within = c("Method"))
knitr::kable(nice(a)) %>% print() # ANOVA results

  # show the matrix of pairwise comparisons
  c <- a %>% emmeans(~ Method) %>% pwpm() %>% .[1:4,1:4] %>% t() # matrix of pairwise comp
  rownames(c) <- c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM")
  colnames(c) <- c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM")
  print(c)

  # p-values
  d <- c %>% t()
  d[lower.tri(d)] <- NA
  diag(d) <- NA # remove the diagonal of estimated marginals
  melted_txt <- d %>% melt(na.rm = TRUE)
  melted_txt$value <- melted_txt$value %>% substr(1,6)
  colnames(melted_txt) <- c('Var1','Var2','txt')

  # coefficients
  c[lower.tri(c)] <- NA
  diag(c) <- 0
  melted_cormat <- c %>% melt(na.rm = TRUE)
  melted_cormat$value <- melted_cormat$value %>% as.numeric()

  melted <- melted_cormat %>% merge(melted_txt, by=c('Var1','Var2'))


  melted %>% ggplot(aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, space = "Lab", #breaks=c(round(min(melted_cormat$value),digits=4),0.0000,round(max(melted_cormat$value),digits=4)),
   name="Diff. in Coef.") +
  theme_minimal()+ 
 theme(axis.title=element_blank(), axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()+ 
geom_text(aes(Var2, Var1, label = txt), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.6, 0.7),
  legend.direction = "horizontal"
  )+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))
}
##############################################################################
```




# (1) Data Loading, Cleaning & Saving
```{r,echo=FALSE}
# dataframe after removing outliers
df <- read.csv("..\\Original\\PGC_PTSD_CT.csv",header=T,sep=",") %>% # 3504 subjects loaded
  filter(Included > 0) %>% # remove rows Emily marked as bad, 3438 subjects remained
  dplyr::select(SubjID:SiteName) %>% # select columns of interest
  group_by(SiteName) %>% # group by site
  mutate_at(names(.)[2:149],SDL_RmOut) %>% # replace outliers with group mean for each ROI.The column name list can be replaced by vars(starts_with("L_")) and vars(starts_with("R_"))
  drop_na() # remove rows with NA, 3410 subjects remained

df$mean <- rowMeans(df[,2:149]) # mean across ROIs


# save Data & Cov for ComBat-GAM run in Python
df$SITE <- df$Site # Site should be SITE for COMBAT-GAMs
write.csv(df[,2:149],'data.csv',row.names=FALSE) # data per ROI
write.csv(df[,c("Age","Gender","Group","SITE")],'subject_info.csv',row.names=FALSE) 

# save Data & Cov for Hierarchical Basian Regression (HBR)
write.table(df[,2],'data.txt',sep='\t',row.names=FALSE,col.names=FALSE) # data per ROI
write.table(df[,"Age"],'cov.txt',sep='\t',row.names=FALSE,col.names=FALSE) 
write.table(df[,c("Gender")]-1,'batch.txt',sep='\t',row.names=FALSE,col.names=FALSE) 

# revise site names
df$SiteName <- df$SiteName %>% str_replace_all(c("ADNIDOD"="ADNIDoD", "AMC"="Amsterdam Medical Center","Columbia"="Columbia University","DeBellis"="Duke University-De Bellis","Duke"="Duke University-Morey","Ghent"="Ghent University","Groningen"="University of Groningen","Grupe"="U.W. Madison-Grupe","GTP"="Emory University-GTP","INTRUST"="INTRuST","Larson"="U.W. Milwaukee-Larson","Leiden"="Leiden University","Mannheim"="University of Mannheim","McLean"="Harvard University-McLean","Minneapolis"="Minneapolis V.A.-Disner","Munster"="University of Münster","Phan"="University of Illinois-Chicago","Rosso"="Harvard University-Rosso","SouthDakota"="University of South Dakota","Stanford"="Stanford University","Stellenbosch"="Stellenbosch University","Toledo"="University of Toledo","UCAS"="UCAS-Beijing","UCT"="University of Cape Town","UNSW"="University of Sydney-Westmead","Uwash"="University of Washington","Waco"="Waco V.A.","WestHaven"="University of New Haven","Yale"="Yale University"))


df0 <- df # df0 is the cleaned data for backup

```

# (2) Harmonization
## (2.1)ComBatHarmonization (standard ComBat)
from https://github.com/Jfortin1/ComBatHarmonization
```{r}
source("ComBatHarmonization/utils.R"); # install some packages first
source("ComBatHarmonization/combat.R") # load R scripts

df <- df0
# Our data
dat <-t(df[,2:149]) # Num. of features x Num. of participants
batch <- df$Site # variables of no interest
age <- df$Age
sex <- df$Gender %>% as.factor()
disease <- df$Group %>% as.factor()
mod <- model.matrix(~age + sex + disease) # variables of interest
combat.harmonized <- combat(dat=dat, batch=batch, mod=mod, parametric=TRUE, eb=TRUE) 
# non-parametric adjustment is time consuming!!!
# Empirical Bayes (eb) is NOT needed when (1) The number of features is substantially smaller than the number of participants or (2) The prior distributions used in ComBat do not fit well the data (3) The site effects are only present for a small subset of features

df1 <- df
df1[,2:149] <- combat.harmonized$dat.combat %>% t() %>% as.data.frame() # harmonized data
df1$mean <- df1[,2:149] %>% rowMeans() # get the mean CT per subject

```


## (2.2) ComBat-GAM
GAMS = Generalized Additive Models
from https://github.com/rpomponio/neuroHarmonize

Run the below codes in Anaconda Prompt not in R Markdown, because there is now no way to install the neuroHarmonize package using R Markdown 
==========
#import pandas as pd
#import numpy as np
#from neuroHarmonize import harmonizationLearn # need to know how to run neuroHarmonize here

#my_data = pd.read_csv('data.csv') # brain data
#my_data = np.array(my_data) # convert into array
#covars = pd.read_csv('subject_info.csv') # covariates of interest.
#my_model, my_data_adj = harmonizationLearn(my_data,covars,smooth_terms=['Age']) # the smooth_terms specifie age as a nonlinear term in the harmonization model

# save harmonized data into csv file
#np.savetxt("neuroHarmonize.csv", my_data_adj, delimiter=",")
==========
```{r,echo=FALSE}
#library(reticulate) # to run ComBat-GAMs
#py_install("pandas")
#py_install("numpy")
#py_install("statsmodels")
df2 <- df0
df2[,2:149] <- read.csv("neuroHarmonize.csv", header = FALSE,sep=",") #
df2 <- df2 %>% ungroup() %>% # drop grouping in df
  mutate(mean = rowMeans(.[,2:149])) # mean across ROIs
```



## (2.3) ComBat++
from https://github.com/ai-med/Dataset-Bias
```{r}
source("Dataset-Bias-master/ComBat++/utils.R");  # install some packages first
source("Dataset-Bias-master/ComBat++/combatPP.R") # load R scripts

# Our data
df <- df0
dat <-t(df[,2:149]) # Num. of features x Num. of participants
batch <- df$Site # variables of no interest
age <- df$Age
sex <- df$Gender %>% as.factor()
disease <- df$Group %>% as.factor()
mod <- model.matrix(~age + sex + disease) # variables of interest

prcomps <- princomp(t(dat)) # PCA analyses
PCs <- predict(prcomps,t(dat))
var_remove <- PCs[,c(1,2)] # variables of no interest

#mod_remove <- model.matrix(~ MFS) # variables of no interest, magnetic field strength (MFS)
#var_remove <- cbind(mod_remove,PCs[,c(1,2)]) # combine variables of no interest

data.harmonized <- combatPP(dat=dat,PC=var_remove,mod=mod,batch=batch,parametric=TRUE,eb=TRUE) # ComBat++

# non-parametric adjustment is time consuming!!!
# Empirical Bayes (eb) is NOT needed when (1) The number of features is substantially smaller than the number of participants or (2) The prior distributions used in ComBat do not fit well the data (3) The site effects are only present for a small subset of features

df3 <- df
df3[,2:149] <- data.harmonized$dat.combat %>% t() %>% as.data.frame() # harmonized data
df3$mean <- df3[,2:149] %>% rowMeans() # get the mean CT per subject

```


## (2.4) Hierarchical Bayesian regression (HBR)
codes from https://github.com/amarquand/PCNtoolkit
instructions from  https://github.com/amarquand/PCNtoolkit/wiki/Normative-Modelling
paper from https://arxiv.org/pdf/2005.12055.pdf

Run the below codes in Anaconda Prompt not in R Markdown 
==========
#import pandas as pd
#import numpy as np
#from pcntoolkit.normative import estimate, evaluate

# python normative.py -c subject_info.txt -k 5 -a blr data.txt

# save harmonized data into csv file
#np.savetxt("neuroHarmonize.csv", my_data_adj, delimiter=",")
==========
```{r,echo=FALSE}
#library(reticulate) # to run ComBat-GAMs
#py_install("pandas")
#py_install("numpy")
#py_install("statsmodels")
df4 <- df0
df4[,2:149] <- read.csv("neuroHarmonize.csv", header = FALSE,sep=",") #
df4 <- df4 %>% ungroup() %>% # drop grouping in df
  mutate(mean = rowMeans(.[,2:149])) # mean across ROIs
```






# (3) Basic statistics and plots

## (3.0a) Table 1, demographic information
```{r,echo=FALSE}
df <- df0 

# re-define the factors' levels
df$Gender <- df0$Gender %>% as.factor() %>% plyr::revalue(c("2"="Female", "1"="Male"))
df$Group  <- df0$Group  %>% as.factor() %>% plyr::revalue(c("2"="Control","1"="PTSD"))

# Statistics of demographic info
## Control
df_CONT <- df %>% filter(Group=="Control") %>% group_by(SiteName) %>% get_summary_stats(Age, type = "mean_sd") # number of subjects & meand/SD of Age
df_CONT <- df %>% filter(Group=="Control" & Gender=='Male') %>% group_by(SiteName) %>% summarise(N_male=n()) %>% merge(df_CONT,by="SiteName",all=TRUE) # add number of males
df_CONT <- df %>% filter(Group=="Control" & Gender=='Female') %>% group_by(SiteName) %>% summarise(N_female=n()) %>% merge(df_CONT,by="SiteName",all=TRUE) # add number of males
## PTSD
df_PTSD <- df %>% filter(Group=="PTSD") %>% group_by(SiteName) %>% get_summary_stats(Age, type = "mean_sd") # number of subjects & meand/SD of Age
df_PTSD <- df %>% filter(Group=="PTSD" & Gender=='Male') %>% group_by(SiteName) %>% summarise(N_male=n()) %>% merge(df_PTSD,by="SiteName",all=TRUE) # add number of males
df_PTSD <- df %>% filter(Group=="PTSD" & Gender=='Female') %>% group_by(SiteName) %>% summarise(N_female=n()) %>% merge(df_PTSD,by="SiteName",all=TRUE) # add number of males
## merge Control and PTSD
df <- merge(df_CONT,df_PTSD,by="SiteName",all=TRUE)
write.csv(df,'Table1.csv',row.names=FALSE) # data per ROI
df
```

## (3.1) plot site-specific age-related changes in cortical thickness (Fig. 1)
```{r,echo=FALSE}
plt1 <- df %>% ggplot(aes(x=Age, y=mean, col=SiteName))+ geom_point(size=1, alpha=0.5)+ labs(y="Cortical Thickness") +geom_smooth(method=lm, se=FALSE)+ theme_minimal()+ theme(legend.title=element_blank(),legend.position="right", legend.text=element_text(size=7))
plt1

```


## (3.2) Boxplot of site effects (Fig. 2)
```{r,warning=FALSE,echo=FALSE}
df <- df0
# Raw
plt1 <- df %>% filter(Group==1) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.y=element_blank(), axis.ticks = element_blank()) + labs(title = "Raw",x="",y="") + ylim(1.85,2.96)+ coord_flip() # raw, PTSD
plt2 <- df %>% filter(Group==2) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.y = element_blank(), axis.ticks = element_blank()) + labs(title = "",x="",y="") + ylim(1.85,2.96)+ coord_flip() # raw, non-PTSD

# ComBat
plt3 <- df1 %>% filter(Group==1) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.y=element_blank(), axis.ticks = element_blank())+ labs(title = "ComBat",x="",y="") + ylim(1.85,2.96)+ coord_flip() # ComBat,PTSD
plt4 <- df1 %>% filter(Group==2) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.y = element_blank(), axis.ticks = element_blank())+ labs(title = "",x="",y="") + ylim(1.85,2.96)+ coord_flip() # ComBat,non-PTSD

#ComBat-GAM
plt5 <- df2 %>% filter(Group==1) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.y=element_blank(), axis.ticks = element_blank())+ labs(title = "ComBat-GAM",x="",y="") + ylim(1.85,2.96)+ coord_flip() # ComBat-GAM,PTSD
plt6 <- df2 %>% filter(Group==2) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none", axis.text.y = element_blank(), axis.ticks = element_blank())+ labs(title = "",x="",y="") + ylim(1.85,2.96)+ coord_flip() # ComBat-GAM,non-PTSD

#ComBat++
plt7 <- df3 %>% filter(Group==1) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank())+ labs(title = "ComBat++,PTSD",x="",y="") + ylim(1.85,2.96)
plt8 <- df3 %>% filter(Group==2) %>% ggplot(aes(x = SiteName,y = mean,col = SiteName,)) + geom_boxplot() + theme(legend.title=element_blank(),legend.text=element_text(size=6),legend.position = "none",axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank())+ labs(title = "ComBat++,non-PTSD",x="",y="") + ylim(1.85,2.96)

#Plots
ggarrange(plt1,plt3,plt5,plt2,plt4,plt6,ncol=3,labels=NULL,common.legend=T) # Raw, ComBat, ComBat-GAM
# ggarrange(plt1,plt2,plt3,plt4,plt5,plt6,ncol=2,labels=NULL,legend="none", common.legend=F) # Raw, ComBat, ComBat-GAM
# ggarrange(plt5,plt7,plt6,plt8, labels=NULL,common.legend=F) # ComBat-GAM, ComBat++
```       

### Fig. 2 related statistical analyses
```{r,echo=FALSE}
# names of ROIs
roilist <- df %>% dplyr::select(L_G_and_S_frontomargin:R_S_temporal_transverse) %>% colnames() #%>% t() %>% as.data.frame()

plist <- data.frame(Statistics = c("tm_PAT_CvG","tm_PAT_CvR","tm_PAT_GvR","pm_PAT_CvG","pm_PAT_CvR","pm_PAT_GvR","tm_CON_CvG","tm_CON_CvR","tm_CON_GvR","pm_CON_CvG","pm_CON_CvR","pm_CON_GvR","tSD_PAT_CvG","tSD_PAT_CvR","tSD_PAT_GvR","pSD_PAT_CvG","pSD_PAT_CvR","pSD_PAT_GvR","tSD_CON_CvG","tSD_CON_CvR","tSD_CON_GvR","pSD_CON_CvG","pSD_CON_CvR","pSD_CON_GvR"))

# 
for (col in roilist[2:length(roilist)]) {

#col="mean"
df <- df0
# # Raw data
dfx_raw_PAT <- df %>% filter(Group==1) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_raw_PAT$Method <- "Raw"
dfx_raw_PAT$nmean <- abs(dfx_raw_PAT$mean-mean(dfx_raw_PAT$mean)) # absolute value of variances

dfx_raw_CON <- df %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_raw_CON$Method <- "Raw"
dfx_raw_CON$nmean <- abs(dfx_raw_CON$mean-mean(dfx_raw_CON$mean))

# ComBat harmonized data
dfx_ComBat_PAT <- df1 %>% filter(Group==1) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBat_PAT$Method <- "ComBat"
dfx_ComBat_PAT$nmean <- abs(dfx_ComBat_PAT$mean-mean(dfx_ComBat_PAT$mean))

dfx_ComBat_CON <- df1 %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBat_CON$Method <- "ComBat"
dfx_ComBat_CON$nmean <- abs(dfx_ComBat_CON$mean-mean(dfx_ComBat_CON$mean))

# ComBat-GAM harmonized data
dfx_ComBatGAM_PAT <- df2 %>% filter(Group==1) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBatGAM_PAT$Method <- "ComBatGAM"
dfx_ComBatGAM_PAT$nmean <- abs(dfx_ComBatGAM_PAT$mean-mean(dfx_ComBatGAM_PAT$mean))

dfx_ComBatGAM_CON <- df2 %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBatGAM_CON$Method <- "ComBatGAM"
dfx_ComBatGAM_CON$nmean <- abs(dfx_ComBatGAM_CON$mean-mean(dfx_ComBatGAM_CON$mean))

# Get t-values & p-values for pairwise comparisons
# 6 outputs are ComBat-vs-ComBatGAM, ComBat-vs-Raw, ComBatGAM-vs-Raw, respectively.
# first 3 outputs are t-values, last 3 outputs are p-values
# P-values are adjusted using Tukey method. with sign to represent the contrast direction.

# PAT
dfx_PAT <- rbind(dfx_raw_PAT, dfx_ComBat_PAT, dfx_ComBatGAM_PAT) # combined for aov

tmp <- aov(nmean ~ Method + Error(SiteName / Method), data = dfx_PAT) %>% emmeans(~ Method) %>% pairs() %>% summary() # ??? This step always meets error when using sapply to run the codes in this chunk
pM_PAT <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate)) # sign of p-values represent the direction of contrast

tmp <- aov(sd ~ Method + Error(SiteName / Method), data = dfx_PAT) %>% emmeans(~ Method) %>% pairs() %>% summary()
pSD_PAT <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate))

# CON
dfx_CON <- rbind(dfx_raw_CON, dfx_ComBat_CON, dfx_ComBatGAM_CON) # combined for aov

tmp <- aov(nmean ~ Method + Error(SiteName / Method), data = dfx_CON) %>% emmeans(~ Method) %>% pairs() %>% summary()
pM_CON <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate)) # sign of p-values represent the direction of contrast

tmp <- aov(sd ~ Method + Error(SiteName / Method), data = dfx_CON) %>% emmeans(~ Method) %>% pairs() %>% summary()
pSD_CON <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate))

plist[,col] <- c(pM_PAT, pM_CON, pSD_PAT, pSD_CON)
}

# save results
write.csv(plist,'plist_Fig2.csv',row.names=FALSE)
```
```{r,echo=FALSE}
# a small function to show t- & p-values (Tukey & fdr corrected)
SDL_tval <- function(txtm, txtp){
  vm <- plist[plist$Statistics==txtm,2:dim(plist)[2]]
  vp <- plist[plist$Statistics==txtp,2:dim(plist)[2]] %>% abs() %>% p.adjust(method="fdr")
  print(paste(txtm,":min=",min(vm)," max=",max(vm),";",txtp,":min=",min(vp)," max=",max(vp)))
  }

# Comparisons of variances
SDL_tval("tm_CON_CvR", "pm_CON_CvR") # CON, ComBat vs Raw
SDL_tval("tm_PAT_CvR", "pm_PAT_CvR") # PAT, ComBat vs Raw

SDL_tval("tm_CON_GvR", "pm_CON_GvR") # CON, ComBat-GAM vs Raw
SDL_tval("tm_PAT_GvR", "pm_PAT_GvR") # PAT, ComBat-GAM vs Raw

SDL_tval("tm_CON_CvG", "pm_CON_CvG") # PAT, ComBat vs ComBat-GAM
SDL_tval("tm_PAT_CvG", "pm_PAT_CvG") # PAT, ComBat vs ComBat-GAM

# Comparisons of SDs
SDL_tval("tSD_CON_CvR", "pSD_CON_CvR") # CON, ComBat vs Raw
SDL_tval("tSD_PAT_CvR", "pSD_PAT_CvR") # PAT, ComBat vs Raw

SDL_tval("tSD_CON_GvR", "pSD_CON_GvR") # CON, ComBat-GAM vs Raw
SDL_tval("tSD_PAT_GvR", "pSD_PAT_GvR") # PAT, ComBat-GAM vs Raw

SDL_tval("tSD_CON_CvG", "pSD_CON_CvG") # PAT, ComBat vs ComBat-GAM
SDL_tval("tSD_PAT_CvG", "pSD_PAT_CvG") # PAT, ComBat vs ComBat-GAM

```


### Fig. 3 related statistical analyses
```{r,echo=FALSE}
# names of ROIs
roilist <- df %>% dplyr::select(L_G_and_S_frontomargin:R_S_temporal_transverse) %>% colnames()

plist <- data.frame(Statistics = c("tm_PAT_CvG","tm_PAT_CvR","tm_PAT_GvR","pm_PAT_CvG","pm_PAT_CvR","pm_PAT_GvR","tm_CON_CvG","tm_CON_CvR","tm_CON_GvR","pm_CON_CvG","pm_CON_CvR","pm_CON_GvR","tSD_PAT_CvG","tSD_PAT_CvR","tSD_PAT_GvR","pSD_PAT_CvG","pSD_PAT_CvR","pSD_PAT_GvR","tSD_CON_CvG","tSD_CON_CvR","tSD_CON_GvR","pSD_CON_CvG","pSD_CON_CvR","pSD_CON_GvR"))


# Age <=20
# # Raw data
df <- df0
df$Method <- "Raw"
df1$Method <- "ComBat"
df2$Method <- "ComBatGAM"

dfx <- rbind(df,df1,df2)

dfx_young_PAT <- dfx %>% ungroup() %>% filter(Group==1 & Age<=20)
dfx_young_CON <- dfx %>% ungroup() %>% filter(Group==2 & Age<=20)

dfx_old_PAT <- dfx %>% ungroup() %>% filter(Group==1 & Age>20)
dfx_old_CON <- dfx %>% ungroup() %>% filter(Group==2 & Age>20)

for (col in roilist[2:length(roilist)]) {

  col = roilist[2]
  

dfx_young_PAT$nmean <- abs(dfx_raw_PAT$mean-mean(dfx_raw_PAT$mean)) # absolute value of variances

dfx_raw_CON <- df %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_raw_CON$Method <- "Raw"
dfx_raw_CON$nmean <- abs(dfx_raw_CON$mean-mean(dfx_raw_CON$mean))

# ComBat harmonized data
dfx_ComBat_PAT <- df1 %>% filter(Group==1) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBat_PAT$Method <- "ComBat"
dfx_ComBat_PAT$nmean <- abs(dfx_ComBat_PAT$mean-mean(dfx_ComBat_PAT$mean))

dfx_ComBat_CON <- df1 %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBat_CON$Method <- "ComBat"
dfx_ComBat_CON$nmean <- abs(dfx_ComBat_CON$mean-mean(dfx_ComBat_CON$mean))

# ComBat-GAM harmonized data
dfx_ComBatGAM_PAT <- df2 %>% filter(Group==1) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBatGAM_PAT$Method <- "ComBatGAM"
dfx_ComBatGAM_PAT$nmean <- abs(dfx_ComBatGAM_PAT$mean-mean(dfx_ComBatGAM_PAT$mean))

dfx_ComBatGAM_CON <- df2 %>% filter(Group==2) %>% group_by(SiteName) %>% get_summary_stats(col,type="mean_sd")
dfx_ComBatGAM_CON$Method <- "ComBatGAM"
dfx_ComBatGAM_CON$nmean <- abs(dfx_ComBatGAM_CON$mean-mean(dfx_ComBatGAM_CON$mean))

# Get t-values & p-values for pairwise comparisons
# 6 outputs are ComBat-vs-ComBatGAM, ComBat-vs-Raw, ComBatGAM-vs-Raw, respectively.
# first 3 outputs are t-values, last 3 outputs are p-values
# P-values are adjusted using Tukey method. with sign to represent the contrast direction.

# PAT
dfx_PAT <- rbind(dfx_raw_PAT, dfx_ComBat_PAT, dfx_ComBatGAM_PAT) # combined for aov

tmp <- aov(nmean ~ Method + Error(SiteName / Method), data = dfx_PAT) %>% emmeans(~ Method) %>% pairs() %>% summary() # ??? This step always meets error when using sapply to run the codes in this chunk
pM_PAT <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate)) # sign of p-values represent the direction of contrast

tmp <- aov(sd ~ Method + Error(SiteName / Method), data = dfx_PAT) %>% emmeans(~ Method) %>% pairs() %>% summary()
pSD_PAT <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate))

# CON
dfx_CON <- rbind(dfx_raw_CON, dfx_ComBat_CON, dfx_ComBatGAM_CON) # combined for aov

tmp <- aov(nmean ~ Method + Error(SiteName / Method), data = dfx_CON) %>% emmeans(~ Method) %>% pairs() %>% summary()
pM_CON <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate)) # sign of p-values represent the direction of contrast

tmp <- aov(sd ~ Method + Error(SiteName / Method), data = dfx_CON) %>% emmeans(~ Method) %>% pairs() %>% summary()
pSD_CON <- c(tmp$t.ratio, tmp$p.value * sign(tmp$estimate))

plist[,col] <- c(pM_PAT, pM_CON, pSD_PAT, pSD_CON)
}

# save results
write.csv(plist,'plist_Fig3.csv',row.names=FALSE)
```

## (3.3) plot mean CT vs. Age (nonlinear curves) (Fig. 3)
Colors and curves for different groups
```{r, warning=FALSE, echo=FALSE}
#df <- dt_filt # data after removing outliers
plt1 <- df %>% ggplot(aes(x = Age, y = mean, col = as.factor(Group))) + geom_point(size = 0.9, alpha = 1) + geom_smooth(method = 'loess', se = T, size = 1, linetype = 1, alpha = 1) + theme_minimal() + labs(title="A", subtitle = "Raw", y="Cortical Thickness") + scale_color_manual(name ="", labels = c("PTSD", "Control"), values = c("pink", "lightblue")) + ylim(1.85,2.96)

plt2 <- df1 %>% ggplot(aes(x = Age, y = mean, col = as.factor(Group))) + geom_point(size = 0.9, alpha = 1) + geom_smooth(method = 'loess', se = T, size = 1, linetype = 1, alpha = 1) + theme_minimal() + labs(title="B", subtitle = "ComBat",y="") + theme(legend.position = "none",axis.text.y = element_blank(), axis.ticks = element_blank())+ scale_color_manual(name ="", labels = c("PTSD", "Control"), values = c("pink", "lightblue")) + ylim(1.85,2.96)

plt3 <- df2 %>% ggplot(aes(x = Age, y = mean, col = as.factor(Group))) + geom_point(size = 0.9, alpha = 1) + geom_smooth(method = 'loess', se = T, size = 1, linetype = 1, alpha = 1) + theme_minimal() + labs(title="C", subtitle = "ComBat-GAM", y = "") + theme(legend.position = "none", axis.text.y = element_blank(), axis.ticks = element_blank()) + scale_color_manual(name ="", labels = c("PTSD", "Control"), values = c("pink", "lightblue")) + ylim(1.85,2.96)

plt4 <- df3 %>% ggplot(aes(x = Age, y = mean, col = as.factor(Group))) + geom_point(size = 1, alpha = .7) + geom_smooth(method = 'loess', formula = y ~ x +x^2, se = T, size = 1.5, linetype = 1, alpha = .7) + theme_minimal() + labs(title = "ComBat++") + theme(legend.position = "none",axis.text.y = element_blank(), axis.ticks = element_blank()) + scale_color_manual(name ="", labels = c("PTSD", "Control"), values = c("pink", "lightblue")) + ylim(1.85,2.96)

ggarrange(plt1,plt2,plt3, ncol=3,labels="",common.legend=T) # multiple plots
ggarrange(plt1,plt2,plt3,plt4, ncol=4,labels="",common.legend=T) # multiple plots
```
## (4) Statistical models across ROIs

### (4.4.1alpha) Model: Group + Age + Sex (no interaction), plotting coefficients & p-values
```{r,echo=FALSE,warning=FALSE}
# No Harmonized
df <- df0
df[df$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group + Age + Gender + (1 |Site))")
Pval1a <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1a <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group + Age + Gender + (1+Age | SITE), control=lmerControl(optimizer='bobyqa'))")
Pval1b <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1b <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat
df1[df1$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df1[,2:149] %>% sapply(SDL_lm, df=df1, Otype="model", ftxt="lm(formula = y ~ Group + Age + Gender)")
Pval2 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef2 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat-GAM
df2[df2$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df2[,2:149] %>% sapply(SDL_lm, df=df2, Otype="model", ftxt="lm(formula = y ~ Group + Age + Gender)")
Pval3 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef3 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat++
df3[df3$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df3[,2:149] %>% sapply(SDL_lm, df=df3, Otype="model", ftxt="lm(formula = y ~ Group + Age + Gender)")
Pval4 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef4 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# effects of Group
Coef_Group <- cbind(Coef1a[,2],Coef1b[,2],Coef2[,2],Coef3[,2],Coef4[,2]) %>% as.data.frame(row.names = rownames(Pval1a))
colnames(Coef_Group) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
Pval_Group <- cbind(Pval1a[,2],Pval1b[,2],Pval2[,2],Pval3[,2],Pval4[,2])
colnames(Pval_Group) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')

# effects of Age
Coef_Age <- cbind(Coef1a[,3],Coef1b[,3],Coef2[,3],Coef3[,3],Coef4[,3]) %>% as.data.frame(row.names = rownames(Pval1a))
colnames(Coef_Age) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
Pval_Age <- cbind(Pval1a[,3],Pval1b[,3],Pval2[,3],Pval3[,3],Pval4[,3])
colnames(Pval_Age) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')

# effects of Sex
Coef_Sex <- cbind(Coef1a[,4],Coef1b[,4],Coef2[,4],Coef3[,4],Coef4[,4]) %>% as.data.frame(row.names = rownames(Pval1a))
colnames(Coef_Sex) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
Pval_Sex <- cbind(Pval1a[,4],Pval1b[,4],Pval2[,4],Pval3[,4],Pval4[,4])
colnames(Pval_Sex) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
```

### Fig. 4D,5D,7D
```{r, echo=FALSE}
# main effect of Group
Coef_Group[,1:4] %>% SDL_heatmap_coef()

# main effect of Age
Coef_Age[,1:4] %>% SDL_heatmap_coef()

# main effect of Sex
Coef_Sex[,1:4] %>% SDL_heatmap_coef()
```



# Plot Group effect
### Fig. 4A,B&C
```{r,echo=FALSE}
dfp <- cbind(Coef_Group,Pval_Group) # new dataframe for plot purpose
dfp <- dfp[order(dfp[,4]),] # sort the values according to the coef. of Combat-GAM (ascending order)
order_group <- order(dfp[,4]) # order of the group effect, to plot group difference of raw value
Region <- rep(1:148,times=4)
Coefficient <- dfp[,1:4] %>% as.matrix() %>% as.vector()
P_value <- dfp[,6:9] %>% as.matrix() %>% as.vector() 
Method <- rep(c('LME (int)','LME (int+slp)','ComBat','ComBat-GAM'),each=148)
plt1 <- data.frame(Region,Coefficient,Method) %>% ggplot(aes(x=Region,y=Coefficient,col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()
plt2 <- data.frame(Region,P_value,Method) %>% ggplot(aes(x=Region,y=-1*log10(P_value),col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()  +ylab('-log10(p-value)') + geom_hline(yintercept=-1*log10(0.05),linetype="dashed", size=1) + geom_hline(yintercept=-1*log10(0.05/148),linetype="solid", size=1)
ggarrange(plt2,plt1, labels=c("A","C"),legend='top',common.legend=T) # multiple plots

## print significant results 
### can also see whether the findings were reported by the other approaches
print(dfp[dfp[,9]<0.05/148,c(4,6,7,8,9)]*148) # ComBat-GAM, 25 regions significant
print(dfp[dfp[,8]<0.05/148,c(3,6,7,8,9)]*148) # ComBat, 6 regions significant
print(dfp[dfp[,7]<0.05/148,c(2,6,7,8,9)]*148) # LME(int+slp), 4 regions significant
print(dfp[dfp[,6]<0.05/148,c(1,6,7,8,9)]*148) # LME(int), 4 regions significant


chi <- c(25, 148-25, 6, 148-6, 4, 148-4, 4, 148-4) %>% matrix(nrow=2, ncol=4, dimnames=list(c("Sig","NoSig"), c("ComBat-GAM","ComBat","LME(int)","LME(int+slp)"))) %>%  chisq.test()

chi$observed


## heatmap of the proportion of regions detected by method#A are also detected by method#B
mat <- matrix(0,4,4,dimnames=list(c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"), c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"))) # make a zero matrix of 4 rows and 4 columns
for (i in c(1,2,3,4)){
  for (j in c(1,2,3,4)){
    # total number of significant regions
    n_total <- dfp %>% .[.[,i+5]<0.05/148,] %>% dim() %>% .[1] 
    # number of both significant regions
    n_both  <- dfp %>% .[.[,i+5]<0.05/148 & .[,j+5]<0.05/148,] %>% dim() %>% .[1]
    # proportion of regions detected by method#i that are also detected by method#j
    mat[i,j] <- n_both/n_total*100 %>% round(digits=1)
  }
}
# heatmap
mat %>% melt() %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=50, limit =c(0,100), name="%") +theme_minimal()+ theme(axis.text.x=element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()+ 
geom_text(aes(Var2, Var1, label=round(value,1)), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = "top",
  legend.direction = "horizontal"
  )+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "right", title.hjust = 0.5))

## BrainNet Viewer files
# LME
p <- Pval_Group[,1] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Group[,1] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Group_LME.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# LMEslp
p <- Pval_Group[,2] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Group[,2] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Group_LMEslp.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# ComBat
p <- Pval_Group[,3] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Group[,3] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Group_ComBat.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# ComBat-GAM
p <- Pval_Group[,4] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Group[,4] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Group_ComBat-GAM.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 
```

# Plot Age effect
### Fig. 5A,B&C
```{r,echo=FALSE}
dfp <- cbind(Coef_Age,Pval_Age) # new dataframe for plot purpose
dfp <- dfp[order(dfp[,4]),] # sort the values according to the coef. of ComBat-GAM (ascending order)
Region <- rep(1:148,times=4)
Coefficient <- dfp[,1:4] %>% as.matrix() %>% as.vector()
P_value <- dfp[,6:9] %>% as.matrix() %>% as.vector() 
Method <- rep(c('LME (int)','LME (int+slp)','ComBat','ComBat-GAM'),each=148)
plt1 <- data.frame(Region,Coefficient,Method) %>% ggplot(aes(x=Region,y=Coefficient,col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()
plt2 <- data.frame(Region,P_value,Method) %>% ggplot(aes(x=Region,y=-1*log10(P_value),col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip() +ylab('-log10(p-value)') + geom_hline(yintercept=-1*log10(0.05),linetype="dashed", size=1) + geom_hline(yintercept=-1*log10(0.05/148),linetype="solid", size=1)
ggarrange(plt2,plt1, labels=c("A","C"),legend='top',common.legend=T) # multiple plots

## print significant results 
print(dfp[dfp[,9]<0.05/148,c(4,6,7,8,9)]*148) # ComBat-GAM, 148 regions significant
print(dfp[dfp[,8]<0.05/148,c(3,6,7,8,9)]*148) # ComBat, 148 regions significant
print(dfp[dfp[,7]<0.05/148,c(2,6,7,8,9)]*148) # LME(int+slp), 78 regions significant
print(dfp[dfp[,6]<0.05/148,c(1,6,7,8,9)]*148) # LME(int), 145 regions significant


c(148, 148-148, 148, 148-148, 145, 148-145, 78, 148-78) %>% matrix(nrow=2, ncol=4, dimnames=list(c("Sig","NoSig"), c("ComBat-GAM","ComBat","LME(int)","LME(int+slp)"))) %>%  chisq.test()


## heatmap of the proportion of regions detected by method#A are also detected by method#B
mat <- matrix(0,4,4,dimnames=list(c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"), c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"))) # make a zero matrix of 4 rows and 4 columns
for (i in c(1,2,3,4)){
  for (j in c(1,2,3,4)){
    # total number of significant regions
    n_total <- dfp %>% .[.[,i+5]<0.05/148,] %>% dim() %>% .[1] 
    # number of both significant regions
    n_both  <- dfp %>% .[.[,i+5]<0.05/148 & .[,j+5]<0.05/148,] %>% dim() %>% .[1]
    # proportion of regions detected by method#i that are also detected by method#j
    mat[i,j] <- n_both/n_total*100 %>% round(digits=1)
  }
}
# heatmap
mat %>% melt() %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=50, limit =c(0,100), name="%") +theme_minimal()+ theme(axis.text.x=element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()+ 
geom_text(aes(Var2, Var1, label=round(value,1)), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = "top",
  legend.direction = "horizontal"
  )+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "right", title.hjust = 0.5))

## BrainNet Viewer files
# LME
p <- Pval_Age[,1] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Age[,1] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Age_LME.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# LMEslp
p <- Pval_Age[,2] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Age[,2] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Age_LMEslp.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# ComBat
p <- Pval_Age[,3] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Age[,3] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Age_ComBat.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# ComBat-GAM
p <- Pval_Age[,4] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Age[,4] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Age_ComBat-GAM.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)
```

# Plot Sex effect
### Fig. 7A,B&C
```{r,echo=FALSE}
dfp <- cbind(Coef_Sex,Pval_Sex) # new dataframe for plot purpose
dfp <- dfp[order(dfp[,4]),] # sort the values according to the coef. of ComBat-GAM (ascending order)
Region <- rep(1:148,times=4)
Coefficient <- dfp[,1:4] %>% as.matrix() %>% as.vector()
P_value <- dfp[,6:9] %>% as.matrix() %>% as.vector() 
Method <- rep(c('LME (int)','LME (int+slp)','ComBat','ComBat-GAM'),each=148)
plt1 <- data.frame(Region,Coefficient,Method) %>% ggplot(aes(x=Region,y=Coefficient,col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()
plt2 <- data.frame(Region,P_value,Method) %>% ggplot(aes(x=Region,y=-1*log10(P_value),col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip() +ylab('-log10(p-value)') + geom_hline(yintercept=-1*log10(0.05),linetype="dashed", size=1) + geom_hline(yintercept=-1*log10(0.05/148),linetype="solid", size=1)
ggarrange(plt2,plt1, labels=c("A","C"),legend='top',common.legend=T) # multiple plots

## print significant results 
print(dfp[dfp[,9]<0.05/148,c(4,6,7,8,9)]*148) # ComBat-GAM, 38 regions significant
print(dfp[dfp[,8]<0.05/148,c(3,6,7,8,9)]*148) # ComBat, 38 regions significant
print(dfp[dfp[,7]<0.05/148,c(2,6,7,8,9)]*148) # LME(int+slp), 28 regions significant
print(dfp[dfp[,6]<0.05/148,c(1,6,7,8,9)]*148) # LME(int), 32 regions significant

# chisq test of the number of significant regions
c(38, 148-38, 38, 148-38, 32, 148-32, 28, 148-28) %>% matrix(nrow=2, ncol=4, dimnames=list(c("Sig","NoSig"), c("ComBat-GAM","ComBat","LME(int)","LME(int+slp)"))) %>%  chisq.test()

## heatmap of the proportion of regions detected by method#A are also detected by method#B
mat <- matrix(0,4,4,dimnames=list(c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"), c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"))) # make a zero matrix of 4 rows and 4 columns
for (i in c(1,2,3,4)){
  for (j in c(1,2,3,4)){
    # total number of significant regions
    n_total <- dfp %>% .[.[,i+5]<0.05/148,] %>% dim() %>% .[1] 
    # number of both significant regions
    n_both  <- dfp %>% .[.[,i+5]<0.05/148 & .[,j+5]<0.05/148,] %>% dim() %>% .[1]
    # proportion of regions detected by method#i that are also detected by method#j
    mat[i,j] <- n_both/n_total*100 %>% round(digits=1)
  }
}
# heatmap
mat %>% melt() %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=50, limit =c(0,100), name="%") +theme_minimal()+ theme(axis.text.x=element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()+ 
geom_text(aes(Var2, Var1, label=round(value,1)), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = "top",
  legend.direction = "horizontal"
  )+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "right", title.hjust = 0.5))

## BrainNet Viewer files
# LME
p <- Pval_Sex[,1] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Sex[,1] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Sex_LME.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# LMEslp
p <- Pval_Sex[,2] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Sex[,2] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Sex_LMEslp.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# ComBat
p <- Pval_Sex[,3] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Sex[,3] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Sex_ComBat.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# ComBat-GAM
p <- Pval_Sex[,4] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_Sex[,4] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_Sex_ComBat-GAM.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 
```



### (4.4.1a) Model: Group * Age + Gender, plotting coefficients & p-values
```{r,echo=FALSE,warning=FALSE}
# No Harmonized
df <- df0
df[df$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group * Age + Gender + (1 |Site))")
Pval1a <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1a <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group * Age + Gender + (1+Age | SITE), control=lmerControl(optimizer='bobyqa'))")
Pval1b <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1b <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat
df1[df1$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df1[,2:149] %>% sapply(SDL_lm, df=df1, Otype="model", ftxt="lm(formula = y ~ Group * Age + Gender)")
Pval2 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef2 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat-GAM
df2[df2$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df2[,2:149] %>% sapply(SDL_lm, df=df2, Otype="model", ftxt="lm(formula = y ~ Group * Age + Gender)")
Pval3 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef3 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat++
df3[df3$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df3[,2:149] %>% sapply(SDL_lm, df=df3, Otype="model", ftxt="lm(formula = y ~ Group * Age + Gender)")
Pval4 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef4 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# effects of Group:Age
Coef_GroupAge <- cbind(Coef1a[,5],Coef1b[,5],Coef2[,5],Coef3[,5],Coef4[,5]) %>% as.data.frame(row.names = rownames(Pval1a))
colnames(Coef_GroupAge) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
Pval_GroupAge <- cbind(Pval1a[,5],Pval1b[,5],Pval2[,5],Pval3[,5],Pval4[,5])
colnames(Pval_GroupAge) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
```


# Plot Group by Age effect
### Fig. 6A,B&D
```{r,echo=FALSE}

# Plot Group:Age Interaction
dfp <- cbind(Coef_GroupAge,Pval_GroupAge) # new dataframe for plot purpose
dfp <- dfp[order(dfp[,4]),] # sort the values according to the coef. of ComBat-GAM (ascending order)
Region <- rep(1:148,times=4)
Coefficient <- dfp[,1:4] %>% as.matrix() %>% as.vector()
P_value <- dfp[,6:9] %>% as.matrix() %>% as.vector() 
Method <- rep(c('LME (int)','LME (int+slp)','ComBat','ComBat-GAM'),each=148)
plt1 <- data.frame(Region,Coefficient,Method) %>% ggplot(aes(x=Region,y=Coefficient,col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()
plt2 <- data.frame(Region,P_value,Method) %>% ggplot(aes(x=Region,y=-1*log10(P_value),col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip() +ylab('-log10(p-value)') + geom_hline(yintercept=-1*log10(0.05),linetype="dashed", size=1) + geom_hline(yintercept=-1*log10(0.05/148),linetype="solid", size=1)
ggarrange(plt2,plt1, labels=c("A","C"),legend='top',common.legend=T) # multiple plots

## print significant results 
print(dfp[dfp[,9]<0.05/148,c(4,9)]) # ComBat-GAM, 5 regions significant
print(dfp[dfp[,8]<0.05/148,c(3,8,9)]) # ComBat, 0 regions significant
print(dfp[dfp[,6]<0.05/148,c(1,6,9)]) # LME(int), 0 regions significant
print(dfp[dfp[,7]<0.05/148,c(2,7,9)]) # LME(int), 0 regions significant

c(5, 148-5, 0, 148-0, 0, 148-0, 0, 148-0) %>% matrix(nrow=2, ncol=4, dimnames=list(c("Sig","NoSig"), c("ComBat-GAM","ComBat","LME(int)","LME(int+slp)"))) %>%  chisq.test()

## heatmap of the proportion of regions detected by method#A are also detected by method#B
mat <- matrix(0,4,4,dimnames=list(c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"), c("LME(int)","LME(int+slp)","ComBat","ComBat-GAM"))) # make a zero matrix of 4 rows and 4 columns
for (i in c(1,2,3,4)){
  for (j in c(1,2,3,4)){
    # total number of significant regions
    n_total <- dfp %>% .[.[,i+5]<0.05/148,] %>% dim() %>% .[1] 
    # number of both significant regions
    n_both  <- dfp %>% .[.[,i+5]<0.05/148 & .[,j+5]<0.05/148,] %>% dim() %>% .[1]
    # proportion of regions detected by method#i that are also detected by method#j
    mat[i,j] <- n_both/n_total*100 %>% round(digits=1)
  }
}
# heatmap
mat %>% melt() %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=50, limit =c(0,100), name="%") +theme_minimal()+ theme(axis.text.x=element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()+ 
geom_text(aes(Var2, Var1, label=round(value,1)), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = "top",
  legend.direction = "horizontal"
  )+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "right", title.hjust = 0.5))

## BrainNet Viewer files
# LME
p <- Pval_GroupAge[,1] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupAge[,1] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupAge_LME.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# LMEslp
p <- Pval_GroupAge[,2] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupAge[,2] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupAge_LMEslp.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# ComBat
p <- Pval_GroupAge[,3] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupAge[,3] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupAge_ComBat.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# ComBat-GAM
p <- Pval_GroupAge[,4] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupAge[,4] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupAge_ComBat-GAM.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

```

### Fig. 6c
```{r, echo=FALSE}
# Age by Group interaction
Coef_GroupAge[,1:4] %>% SDL_heatmap_coef()
```




### (4.4.1b) Model: Group * Gender + Age, plotting coefficients & p-values
```{r,echo=FALSE,warning=FALSE}
# No Harmonized
df <- df0
df[df$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group * Gender + Age + (1 |Site))")
Pval1a <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1a <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

Modelx <- df[,2:149] %>% sapply(SDL_lm, df=df, Otype="model", ftxt="lmer(formula = y ~ Group * Gender + Age + (1+Age | SITE), control=lmerControl(optimizer='bobyqa'))")
Pval1b <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef1b <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat
df1[df1$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df1[,2:149] %>% sapply(SDL_lm, df=df1, Otype="model", ftxt="lm(formula = y ~ Group * Gender + Age)")
Pval2 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef2 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat-GAM
df2[df2$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df2[,2:149] %>% sapply(SDL_lm, df=df2, Otype="model", ftxt="lm(formula = y ~ Group * Gender + Age)")
Pval3 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef3 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# ComBat++
df3[df3$Group==2,'Group'] = 0 # for the ease of linear model, PTSD=1, Control=0
Modelx <- df3[,2:149] %>% sapply(SDL_lm, df=df3, Otype="model", ftxt="lm(formula = y ~ Group * Gender + Age)")
Pval4 <- Modelx %>% sapply(SDL_cp, para="Pr(>|t|)") %>% t() %>% as.data.frame() # p values
Coef4 <- Modelx %>% sapply(SDL_cp, para="Estimate") %>% t() %>% as.data.frame() # estimates

# effects of Group:Sex
Coef_GroupSex <- cbind(Coef1a[,5],Coef1b[,5],Coef2[,5],Coef3[,5],Coef4[,5]) %>% as.data.frame(row.names = rownames(Pval1a))
colnames(Coef_GroupSex) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
Pval_GroupSex <- cbind(Pval1a[,5],Pval1b[,5],Pval2[,5],Pval3[,5],Pval4[,5])
colnames(Pval_GroupSex) <- c('LME','LME+Slope','ComBat','ComBat-GAM','ComBat++')
```

# Plot Group:Sex Interacton
### Fig. 8A,B&D
```{r,echo=FALSE}
dfp <- cbind(Coef_GroupSex,Pval_GroupSex) # new dataframe for plot purpose
dfp <- dfp[order(dfp[,4]),] # sort the values according to the coef. of ComBat-GAM (ascending order)
Region <- rep(1:148,times=4)
Coefficient <- dfp[,1:4] %>% as.matrix() %>% as.vector()
P_value <- dfp[,6:9] %>% as.matrix() %>% as.vector() 
Method <- rep(c('LME (int)','LME (int+slp)','ComBat','ComBat-GAM'),each=148)
plt1 <- data.frame(Region,Coefficient,Method) %>% ggplot(aes(x=Region,y=Coefficient,col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip()
plt2 <- data.frame(Region,P_value,Method) %>% ggplot(aes(x=Region,y=-1*log10(P_value),col=Method)) + geom_point(alpha = 0.7) + geom_smooth(method = "loess", alpha = 0.05, size = 1, span = 1) + theme_bw() + theme(legend.position = "right") + scale_color_npg() + scale_x_reverse() + coord_flip() +ylab('-log10(p-value)') + geom_hline(yintercept=-1*log10(0.05),linetype="dashed", size=1) + geom_hline(yintercept=-1*log10(0.05/148),linetype="solid", size=1)
ggarrange(plt2,plt1, labels=c("A","C"),legend='top',common.legend=T) # multiple plots

## print significant results 
print(dfp[dfp[,9]<0.05/148,c(4,9)]) # ComBat-GAM, 0 regions significant
print(dfp[dfp[,8]<0.05/148,c(3,8,9)]) # ComBat, 0 regions significant
print(dfp[dfp[,6]<0.05/148,c(1,6,9)]) # LME(int), 0 regions significant
print(dfp[dfp[,7]<0.05/148,c(2,7,9)]) # LME(int), 0 regions significant

c(0, 148-0, 0, 148-0, 0, 148-0, 0, 148-0) %>% matrix(nrow=2, ncol=4, dimnames=list(c("Sig","NoSig"), c("ComBat-GAM","ComBat","LME(int)","LME(int+slp)"))) %>%  chisq.test()

## BrainNet Viewer files
p <- Pval_GroupSex[,4] %>% log10()*(-1)
cof <- Coef_GroupSex[,4]
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0)
p_size  <- Coef_GroupSex[,4]
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupSex.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# LME
p <- Pval_GroupSex[,1] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupSex[,1] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupSex_LME.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# LMEslp
p <- Pval_GroupSex[,2] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupSex[,2] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupSex_LMEslp.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F)

# ComBat
p <- Pval_GroupSex[,3] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupSex[,3] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupSex_ComBat.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

# ComBat-GAM
p <- Pval_GroupSex[,4] %>% log10()*(-1)
p_color <- ifelse(p>-1*log10(0.05/148), 1, 0) # 1=display, 0=hide
p_size  <- Coef_GroupSex[,4] # values to be plotted
nf <- cbind(atlas[,2:4],p_color,p_size,atlas[,5]) 
write.table(nf, "node_GroupSex_ComBat-GAM.txt", append = FALSE, sep = " ", dec = ".", row.names = F, col.names = F) 

```

### Fig. 8c
```{r, echo=FALSE}
# Age by Group interaction
Coef_GroupSex[,1:4] %>% SDL_heatmap_coef()
```

